---
title: "Day 14"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
meta <- read.csv("airway_metadata.csv", stringsAsFactors = F)
counts <- read.csv("airway_scaledcounts.csv", stringsAsFactors = F)

# stringAsFactors = F keeps R from changing the gene names into factors 
```
How many genes are in this dataset?
```{r}
head(counts)
nrow(counts)

```

There are 38,694 genes in the dataset 
```{r}
head(meta)
```
How many control cell lines are in this dataset? 
```{r}
#Check if the colnames of "counts" are the same as id column in 'metadata'
colnames(counts)

meta$id
#remove the first column and check to see if the names are equal in both datasets 
all(colnames(counts)[-1] == meta$id)
#'all' checks if they are ALL true. If there is one false it would return FALSE

#now, aswer the question, how many control cell lines are there?

table(meta$dex)
```

Access just the control counts data so we can calculate an average counts value for each gene in these control samples 
```{r}
control <- meta[meta[,"dex"]=="control",]
control
```
Now, we want to get the cols in the counts with these 'control$id' colnames 
```{r}
# calculates the mean value for every row (gene)
control.mean <- rowSums(counts[, control$id]/length(control$id))
head(control.mean)
# add the names 
names(control.mean) <- counts$ensgene
head(control.mean)
```
Now, do the same for the treated samples 
```{r}
treated <- meta[meta[,"dex"]=="treated",]
head(treated)
```
```{r}
treated.mean <- rowSums(counts[, treated$id]/length(treated$id))
head(treated.mean)
names(treated.mean) <- counts$ensgene
head(treated.mean)
```

Combine the control and treated data into a single data frame
```{r}
mean.counts <- data.frame(treated.mean, control.mean)
head(mean.counts)
```
Now, plot the means of the control and treated 
```{r}
plot(treated.mean ~ control.mean, pch=20, col=rainbow(10), log="xy")

# log = "xy" log transforms the data to spread out the data points 
```

```{r}
mean.counts$log2fc <- log2(mean.counts$treated.mean/mean.counts$control.mean)
head(mean.counts)
```
NaN is returned when you divide by 0 and try to take the log. The -INf is returned when you try and take the log of 0. 
```{r}
mean.counts[,1:2]==0
to.rm <- unique(which(mean.counts[,1:2]==0, arr.ind=TRUE)[,1])
# remove the counts that are NaN or -Inf
my.counts <- mean.counts[-to.rm, ]
head(my.counts)
```
```{r}
up.inds <- my.counts$log2fc > 2
down.inds <- my.counts$log2fc < (-2)
head(up.inds)
length(which(up.inds==T))
length(which(down.inds==T))

sum(up.inds)
```
ADD THE ANNODATION DATA!!!!!!!!!!!
```{r}
anno <- read.csv("annotables_grch38.csv")
head(anno)
```

NOW MERGE THEM!!!!!! USE THE *MERGE* FUNCTION TO COMBINE THE ANNOTATION DATA WITH THE COUNTS DATA!!!!!!!!!
```{r}
merge(x=my.counts,  y=anno,  by.x = "row.names", by.y ="ensgene")

```

```{r}

```

