---
title: "Day07:Functions and packages"
author: "Tiani Louis"
date: "4/24/2019"
output: github_document 
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## More on function writing 
```{r}
source("http://tinyurl.com/rescale-R")
```

Test the *rescale()* function
```{r}
rescale(1:10)
```

```{r}
x <- c(1:10, "string")
!is.numeric(x)
```
## Function practice
Write a function to identify NA elements in two vectors
Start with a simple example where I know what the answer should be 
```{r}
x <- c( 1, 2, NA, 3, NA)
y <- c(NA, 3, NA, 3, 4)
```
```{r}
is.na(x)
is.na(y)
```
# this will tell you when both x and y are NA

```{r}
is.na(x) & is.na(y)
```
Take the sum to find how many 
```{r}
sum( is.na(x) & is.na(y))
```

Take this and use it as the body of the function 
```{r}
both_na <- function(x,y) {
if(length(x) != length(y)) {
stop("UHHHH, They really should be the same length")
 }
sum( is.na(x) & is.na(y))  
}
```

TEST IT!
```{r}
both_na(x,y)
```
```{r}
both_na(c(NA,NA,NA), c(1,NA,NA))

```
These are different lengths and this code should throw an error > R will recycle the length of the first vector to produce an answer
```{r}
# both_na(c(NA,NA,NA), c(1,NA,NA,NA))
```
Check the length of the vectors using length()
```{r}
length(x) == length(y)
```
Add some cute extras!

```{r}
x <- c( 1, 2, NA, 3, NA)
y <- c(NA, 3, NA, 3, 4)

both_na <- function(x,y) {
  if(length(x) != length(y)) {
 stop("UHHHH, They really should be the same length")
 }
sum( is.na(x) & is.na(y))  
}

both_na(x,y)
```
```{r}
# student 1
s_1 <- c(100,100,100,100,100,100,100,90)

#student 2
s_2 <- c(100, NA, 90, 90,90,90, 97, 80)
```

```{r}
grade <- function(x) {
  min_g <- min(x)
 sum_g <- sum(x) - min_g
 average <- sum_g/(length(x)-1)
return(average)
}
```

```{r}
grade(s_1)
grade(s_2)
```
```{r}
grade2 <- function(x) {
  min_g <- min(x)
 average <- mean(x, na.rm =T)
return(average)
}
```


```{r}
grade2(s_2)

```
```{r}
grade3 <- function(x) {
  min_g <- min(x)
  sum_g <- sum(x) - min_g
  average <- sum_g/(length(x)-1)
  if (is.na(x)) {
  min_g <- min(x)
 average2 <- mean(x, na.rm =T)
return(average2)
  }
 
}
```

```{r}
grade3(s_2)
```
```{r}
grade <-function(x) {
  (sum(x, na.rm=T) - min(x, na.rm=T))/(length(x)-1)
}
```


```{r}
grade(s_2)
```
```{r}
# student_homework <- read.csv("~/Desktop/BGGN213/Day07/student_homework.csv")
```

```{r}
url <- "https://tinyurl.com/gradeinput"
students <- read.csv(url, row.names = 1)
head(students)
```
```{r}
grade(students[5,])
```
```{r}
ans <- apply(students, 1, grade)
```

```{r}
sort(ans, decreasing =T)
```
The function to end all functions 
find the intersection of two samples
```{r}
x <- df1$IDs
y <- df2$IDs
z <- df3$IDs
intersect(x,y)


```
```{r}
x
y
z

 x[x %in% z]
```
column bind cbind() row bind rbind()
%in% finds the common elements between two vectors 
```{r}
gene_intersect <- function(x, y) {
  cbind(x[x %in% y], y[y %in% x])
}
```

```{r}
merge(df1, df2, by="IDs")
```


```{r}
# ggplot(df1, aes( x = IDs)) + geom_path(aes(y = exp), color="red")

```
