---
title: "Day 11: Structural Bioinformatics (Pt1)"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Revisit the PDB 

##**Question 1: Download a CSV file from the PDB site (accessible from “Analyze” -> “PDB Statistics” >
“by Experimental Method and Molecular Type”. Move this CSV file into your RStudio project
and determine the percentage of structures solved by X-Ray and Electron Microscopy. Also can
you determine what proportion of structures are protein? Aim to have a rendered GitHub
document with working code that yields your answers**

Download a CSV file from: https://www.rcsb.org/stats/summary
```{r}
# percent of xray structures 
db <- read.csv("Data Export Summary.csv", row.names = 1)
head(db)

sum(db$Total)

rowSums(db)
(db$Total/sum(db$Total)) * 100 



# proportion of protein 
(sum(db$Proteins)/sum(db$Total)) *100

```
## Percent Xray : 89.35%
## Percent Electron Microscopy: 2.06%
## Proportion of Protein : 92.76461%

### **Q2: Type HIV in the PDB website search box on the home page and determine how many
HIV-1 protease structures are in the current PDB?**

## 1,157 protease structures 

```{r}
library(bio3d)
library(bio3d.view)
library(rgl)
pdb <- read.pdb(file = "1hsg")
pdb
```

```{r}
pdb$seqres
```
```{r}
ca.ins <- atom.select(pdb, "calpha")

atom.select(pdb, resno = 10)

pdb$atom[1:2, c("eleno", "elety", "x","y","z")]
```
Select protein only and write out a PDB file titled "1HSE_Protein.pdb"
Select ligand/drug and write out a PDB file titled "1HSE_Ligand.pdb"
```{r}
protein <- atom.select(pdb, "protein", value = T)
protein

ligand <- atom.select(pdb, "ligand", value = T)
ligand

write.pdb(protein, file = "1HSE_Protein.pdb")
write.pdb(ligand, file="1HSE_Ligand.pdb")
```

```{r}
view(pdb, "overview", col="sse")

```

```{r}
view(ligand)
```
## Section 6. Working with multiple PDBs 
```{r}
ids <- c("1TND_B","1AGR_A","1TAG_A","1GG2_A","1KJY_A","4G5Q_A")
files <- get.pdb(ids, split = TRUE)
```

```{r}
pdbs <- pdbaln(files, fit = T)

```

```{r}
pc.xray <- pca(pdbs)
plot(pc.xray)

```
```{r}
pc1 <- mktrj(pc.xray, pc=1, file="pc_1.pdb")
library(bio3d.view)
# Structural displacements captured by PC1
view(pc1)
# The rglwidget() function from the rgl
# package will show output in your Rmd
# notebook and rendered html_output
# documents
library(rgl)
#rglwidget(pc1)
```

