---
title: "Day 11: Structural Bioinformatics (Pt1)"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
## Revisit the PDB 

#**Question 1: Download a CSV file from the PDB site (accessible from “Analyze” -> “PDB Statistics” >
“by Experimental Method and Molecular Type”. Move this CSV file into your RStudio project
and determine the percentage of structures solved by X-Ray and Electron Microscopy. Also can
you determine what proportion of structures are protein? Aim to have a rendered GitHub
document with working code that yields your answers**

Download a CSV file from: https://www.rcsb.org/stats/summary
```{r}
# percent of xray structures 
db <- read.csv("Data Export Summary.csv", row.names = 1)
head(db)

sum(db$Total)

rowSums(db)
(db$Total/sum(db$Total)) * 100 



# proportion of protein 
(sum(db$Proteins)/sum(db$Total)) *100

```
## Percent Xray : 89.35%
## Percent Electron Microscopy: 2.06%
## Proportion of Protein : 92.76461%

### **Q2: Type HIV in the PDB website search box on the home page and determine how many
HIV-1 protease structures are in the current PDB?**

## 1,157 protease structures 

```{r}
pdb <- read.pdb(file = "1hsg.pdb")
pdb
```

```{r}
pdb$seqres
```
```{r}
ca.ins <- atom.select(pdb, "calpha")

atom.select(pdb, resno = 10)


```



