---
title: "Day 12"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(bio3d)
library(rgl)

```

```{r}
hsg <- get.pdb("1hsg")
```
```{r}
hiv <- read.pdb(hsg)
hiv
```

**Q1: What is the name of the two non protein resid values in this structure? What does resid
correspond to and how would you get a listing of all reside values in this structure? **

A1: HOH (127),  MK1(1)

Resid = "residuals"
```{r}
#select protein and ligand only 
prot <- atom.select(hiv, "protein", value = T)
prot
write.pdb(prot, file = "1hsg_protein.pdb")

lig <- atom.select(hiv, "ligand", value = T)
lig
write.pdb(lig, file = "1hsg_ligand.pdb")
```
## Add Hydrogen and charges in ADT 

We opened our pdb in AutdocTools and added hydrogen and atom types for docking calculations 
## Run docking 
We will use AutoDoc Vina here at the UNIX command line 


## Make a grid box that encompasses the docking area
```{r}
res <- read.pdb("all.pdbqt", multi=T)
res
```

```{r}
res <- read.pdb("all.pdbqt", multi=TRUE)
write.pdb(res, "results.pdb")
```

```{r}
# res <- read.pdb("all.pdbqt", multi=TRUE)
ori <- read.pdb("1hsg_ligand.pdbqt")
rmsd(ori, res)
```
```{r}
pdb <- read.pdb("1hel")
modes <- nma( pdb )
m7 <- mktrj(modes, mode=7, file="mode_7.pdb")
```

